---
title: "MATH 216 Homework 2 Shiny App"
author: "Bianca Gonzalez"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(babynames)
library(ggplot2movies)
library(tidyverse)

```


## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.


In the file `HW-2_Shiny_App.Rmd`, build the Shiny App discussed in Lec09 on
Monday 10/3: Using the `movies` data set in the `ggplot2movies` data set, make a
Shiny app that

* Plots budget on the x-axis and rating on the y-axis
* Instead of having a radio button to select the genre of movie (`Action`,
`Animation`, `Comedy`, etc), have a radio button that allows you to toggle
between comedies and non-comedies. This app should be simpler.

```{r eruptions, echo=FALSE}

library(ggplot2movies)
Genre_movies <- movies %>% 
    filter(budget != is.na(budget)) %>% 
    mutate(bleep = ifelse(Comedy == 1 , TRUE, FALSE))
      #dataset select comedy

inputPanel(
  radioButtons("Genre", "Comedy?", choices = c("Yes", "No"))
                                              #multiple inputs 
)

#, "Non-Comedies" = c("Action", "Drama", "Romance", "Documentary")
renderPlot({
  # filter(name == input$name & year >= input$start_year & year <= input$end_year )
  
  #create a variable to translate the true or false to yes or no.
  trans <- input$Genre == "Yes"
  
  Genre <- Genre_movies %>% 
    filter(bleep == trans) %>%  #new column, filter out the true or false options
      ggplot(aes(x=budget, y= rating)) + 
        geom_point() +
            geom_smooth()
  Genre
})
```
